\begin{acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I would like to thank the following people who, with their love and
support, encouraged and enabled me to finish this dissertation.

Giovanni, if he knows it or not, is the reason that I became addicted
to computer security: From the moment that I took his undergrad
security class I was hooked. I am forever indebted to him because he
has constantly invested his time in me. First, by inviting me to join
his hacking club. Then, he took a chance on mentoring a Master's
student, and, upon graduation for my Master's degree, told me that I
could ``come back for the real thing.'' One year later I did, and it
was an experience I will never regret. I hope that I always have the
enthusiasm and energy that Giovanni brings to research and life. He is
truly a role model.

From Chris, I learned a great deal about what it means to be an
academic and a scientist. He is able to focus so intensely on the
details of the project while not loosing sight of the bigger
picture---if I am able to do this half as well I will consider myself
a success. He constantly inspires and encourages me to heights I never
dreamed possible.

I would never have been able to finish this dissertation without the
help and encouragement of all the past and current seclab members. I
am forever grateful to the now departed members of the seclab who were
here when I started my Masters. You took me under your wing, taught
me, and created and infused within me the \emph{seclab culture.} Of
those I thank: Wil, Vika, Sean, Nick, Brett, Lorenzo, Fede, Martin,
Max, and especially Marco, for his wisdom and guidance.

The only way I was able to stay sane during my PhD was because of my
fellow sec\-lab members. We forged a bond during those 3am deadlines,
iCTF all-nighters, walks to Freebirds!, costume parties, and soccer
games---a bond which makes us brothers-in-arms. In no particular
order, thanks to: Gianluca, Antonio, Luca, Alexandros, Gorkem, Ali,
Patrick, Kevin, Jacopo, Dhilung, Kyle, Yan, Fish, Bob, Ludo, Manuel,
Gregoire, and Bryce.

A very special thanks to my Mom, Dad, and brother for their love,
support, and constant ribbing and teasing.

And finally, thanks to Becca for being my rock.

\end{acknowledgements}
